
% Cameron Bracken's Resume
% Created: 1 Sep 2007
% Last Modified: 25 Sep 2008

\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage{palatino}
%\usepackage[T1]{fontenc}
\usepackage{mathpazo}
\usepackage{courier}

\pagestyle{empty}
\geometry{letterpaper,tmargin=1.3cm,bmargin=1.3cm,lmargin=1.3cm,rmargin=1.3cm,headheight=0in,headsep=0in,footskip=0in}
\usepackage{hyperref}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Cameron Bracken}
\newcommand{\addr}{12 E 15th St. Appt. 2}
\newcommand{\phone}{707.825.6787}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}\Huge\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\vspace{3pt}
	{\Large#1}
	\begin{itemize}
	\vspace{2pt}
}{
	\end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-4pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-1pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 \\
	\textit{#3}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

%\fontfamily{phv} \selectfont

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

\vspace{-1pt} {\small \textit{\addr} \hfill \href{mailto:cwb12@humboldt.edu}{\texttt{cwb12@humboldt.edu}}}\\
\vspace{-1pt} {\small\textit{\phone} \hfill \href{http://cbracken.info/}{\texttt{http://cameron.bracken.bz/}}}


\vspace{8 pt}


%%%%%%%%%%%%%%%%%%%%%%%
%\begin{ressection}{Goal}
    
    
%      \resitem{Obtain a Summer 2008 internship at Sandia National %Laboratories working on fluid related statistical or physical modeling.}
    

%\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{\scshape Education}

	\begin{ressubsec}{Humboldt State University}{Arcata, CA}{Majoring in Environmental Resources Engineering and Applied Mathematics}
		\ressubitem{GPA: 3.5 (overall), 3.5 (ERE major), 3.80 (Math major)}
		\ressubitem{Projected Graduation Date: May, 2009}
		\ressubitem{\begin{normalsize}\textit{Selected Courses}: Computational Methods For Engineers 1, 2, 3,
Environmental Systems Engineering, 
Probabilistic Analysis of Environmental Systems, 
Environmental Monitoring and Data Analysis, 
Fluid Mechanics, 
Advanced (vector) calculus, 
ODEs, 
PDEs, 
Applied Stochastic Processes,
River Hydraulics, 
Transport Phenomena, 
Thermodynamics, 
Dynamical Systems, 
Advanced Numerical Methods, 
Hydrology, 
Water Quality and Environmental Health,
Hydrology 2 (time series analysis).
\end{normalsize}}
	\end{ressubsec}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{\scshape Experience}

	\begin{ressubsec}{National Weather Service Student Researcher}{Eureka, CA}{Summer 2008 to present}
		\ressubitem{Worked in a team to develop bar forecast for San Francisco Bay.}
		\ressubitem{Prepared the Advanced Circulation (ADCIRC) and Simulating Waves Nearshore (SWAN) models.}
		\ressubitem{Worked within and extended automated forecast framework.}
		\ressubitem{Developed web interface to model results via Adobe Flex.}
	\end{ressubsec}

	\begin{ressubsec}{Environmental Fluids Research Experience for Undergraduates}{Unv. of Colorado, Boulder}{Summer 2007}
		\ressubitem{Mentored by Dr. Balaji Rajagopalan in efforts to develop multi-site streamflow forecast framework.}
		\ressubitem{Statistical analysis with R and MATLAB, data maniulation.}
		\ressubitem{Work presented at American Geophysical Union Fall 2007 Conference.}
	\end{ressubsec}

	\begin{ressubsec}{Hydrology/Hydraulics Student Research Assistant}{Humboldt State University}{ Fall 2006 to Summer 2008}
		\ressubitem{Assisted the research of Dr. Margaret Lang for CalTrans relating to culvert fish passage.}
		\ressubitem{Performed flume experiments on scale models of culverts, data analysis, culvert surveying.}
	\end{ressubsec}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{\scshape Skills}
    
    \begin{reslist}{Modeling}
      \resitem{Experience implementing: finite differences, finite elements, optimization, statistical forecasting, time series modeling, Monte Carlo simulation.}
      \resitem{Experience with specific models: ADCIRC, SWAN, MODFLOW, RMA2, HEC-RAS, HEC-HMS.}
    \end{reslist}

	\begin{reslist}{Operating Systems:}
		\resitem{Proficient with Mac OS 9 and X, Windows XP and Vista, Linux (Suse, Ubuntu, Fedora).}
    \end{reslist}

	\begin{reslist}{Computer Languages and Programs:}

		\resitem{Proficient with Fortran 90, Matlab, R, \LaTeX, Excel, Html, Adobe Flex.}
		\resitem{Familiar with Fortran 77, Perl, Python, PHP, CSS, MySQL, C, Adobe Illustrator, Adobe Photoshop.}

	\end{reslist}



\end{ressection}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{\scshape Awards}

	\resitem{Roscoe-Schneller Award for outstanding potential in environmental resources engineering, Spring 2007 (\$500).}

	\resitem{Robert S. Chambers Award for academic achievement in mathmatics, Spring 2007 (\$500).}

	\resitem{Honorable mention, 2007 COMAP Mathematical Contest in Modeling (MCM).}
	
	\resitem{Honorable mention, 2008 COMAP Mathematical Contest in Modeling (MCM).}


\end{ressection}

\begin{ressection}{\scshape References}

\resitem{Troy Nicolini\\
Warning Coordination Meteorologist\\
NOAA/NWS\\
Eureka Weather Forecasting Office\\
Phone: (707) 443-6484 ext. 223\\
E-Mail: \href{mailto:troy.nicolini@noaa.gov}{\texttt{troy.nicolini@noaa.gov}}}

\resitem{Dr. Balaji Rajagopalan\\
Associate Professor\\
Dept. of Civil, Environmental and Architectural Engg.\\
University of Colorado Boulder\\
Phone: (303) 492-5968\\
E-mail: \href{mailto:balajir@spot.colorado.edu}{\texttt{balajir@spot.colorado.edu}}}

\resitem{Dr. Brad Finney\\
Professor\\
Environmental Resources Engineering\\
Humboldt State University, California\\
Phone: (707) 826-3918
E-mail: \href{mailto:baf1@humboldt.edu}{\texttt{baf1@humboldt.edu}}}

\end{ressection}

\end{document}
